%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%
\RequirePackage{fix-cm}
%
\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{times}
\usepackage{url}
\usepackage{color}
\definecolor{Orange}{rgb}{1,0.5,0}
\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

% In the original styles from ACM, you would have needed to
% add meta-info here. This is not necessary for AAMAS 2014  as
% the complete copyright information is generated by the cls-files.


\title{Human-Agent Collaboration for Disaster Response}

% AUTHORS


% For initial submission, do not give author names, but the
% tracking number, instead, as the review process is blind.

% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

%\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%

% \author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
% 1st. author
\author{XX,YY,ZZ}
\author{Sarvapali D. Ramchurn \and Feng Wu \and Wenchao Jiang \and Joel Fischer \and Steve Reece \and Stephen Roberts \and Tom Rodden \and Chris Greenhalgh \and  Nicholas R. Jennings 
}

%\authorrunning{Short form of author list} % if too long for running head
%

%\institute{XX \at
%              XX\\
%              \email{\{XX\}}           %  \\
%           \and
%           YY \at
%              YY\\
%		\email{\{YY\}}
%\and
%           ZZ \at
%             ZZ\\
%		\email{\{ZZ\}}}

\institute{Sarvapali D. Ramchurn, Feng Wu, and Nick Jennings \at
              Electronics  and Computer Science, 
	    University of Southampton, UK\\
              \email{\{sdr1,fw1e11,nrj\}@soton.ac.uk}           %  \\
           \and
           Wenchao Jiang, Joel Fischer, Chris Greenhalgh, and Tom Rodden \at
              Mixed Reality Lab, 
		University of Nottingham,
		Nottingham, UK\\
		\email{\{psxwj,jef,cmg,tar\}@cs.nott.ac.uk}
\and
           Steve Reece and Stephen Roberts \at
              Pattern Recognition Group, 
		University of Oxford,
		Oxford, UK\\
		\email{\{reece,roberts\}@robots.ox.ac.uk}}

%% There's nothing stopping you putting the seventh, eighth, etc.
%% author on the opening page (as the 'third row') but we ask,
%% for aesthetic reasons that you place these 'additional authors'
%% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
%\date{30 July 1999}
%% Just remember to make sure that the TOTAL number of authors
%% is the number that will appear on the first page PLUS the
%% number that will appear in the \additionalauthors section.
\date{Received: date / Accepted: date}
\maketitle

\begin{abstract}
In the aftermath of major disasters, first responders are typically
overwhelmed with large numbers of, spatially distributed, search and
rescue tasks, each with their own requirements. Moreover, responders
have to operate in highly uncertain and dynamic environments where new
tasks may appear and hazards may be spreading across the disaster
space. Hence, rescue missions may need to be re-planned as new
information comes in, tasks are completed, or new hazards are
discovered. Hence, finding an optimal allocation of resources to
complete all the tasks is a major computational challenge. Indeed,  a
number of agent-based solutions have been developed to help human
commanders perform such planning tasks. However, studies have shown
that, unless these solutions minimise the cognitive burden imposed on
human commanders and first responders, they may hinder task
performance rather than help.  It is therefore crucial to deploy such
agent-based planning solutions alongside human commanders in order to
uncover the interactional issues that arise. Hence, in this paper, we
use decision theoretic techniques to solve the task allocation problem
posed by emergency response planning and then deploy our solution as
part of an agent-based planning tool in  real-world field trials. By
so doing, we are able to study the interactional issues that arise
when humans are guided by an agent. In more detail, we develop an
algorithm, based on a  Multi-Agent Markov Decision Process
representation of the task allocation problem and show that it
outperforms standard benchmarks from the literature. We then integrate
the algorithm into a planning agent that responds to requests for
tasks from  participants in a mixed-reality location-based game,
called AtomicOrchid, that simulates disaster response settings in the
real-world.  We then run a number of trials of our planning agent and
compare it against a purely human driven system. Our  analysis of
these trials show that human commanders adapt to the planning agent by
taking on a more supervisory role and that, by providing humans with the flexibility of requesting plans from the agent, allows them to perform more tasks more efficiently than using purely human interactions to allocate tasks. We also discuss how such flexibility could lead to poor performance if left unchecked.  \end{abstract}

% Note that the category section should be completed after reference to the ACM Computing Classification Scheme available at
% http://www.acm.org/about/class/1998/.

\keywords{Human-Agent Interaction, Human-Agent Collectives, Disaster Response.}

\input{introduction.tex}
\input{background.tex}
\input{scenario.tex}
\input{coordination.tex}
\input{atomicorchid.tex}

\input{conclusions.tex}

\bibliographystyle{abbrv}

{

\bibliography{citations}
}

\newpage
\appendix
\input{appendix}

\end{document}
